\cvwrapper{fancy}{Cover Letter}{

I am applying for the experimentalist Assistant Physicist  position, Requisition \#323613.  I am currently employed as a postdoctoral research fellow at TRIUMF.

A major responsibility associated with this position is the commissioning of the EMMA spectrometer.
The last four years of my doctoral thesis work involved the development, commissioning, and operation of the Helical Orbit Spectrometer (HELIOS) at Argonne National Laboratory.  In addition to the mechanical and technical aspects of this project, a major component of my work was the development of the computer code for acquisition, calibration and analysis of HELIOS data.  I have published the results of the commissioning of HELIOS in %a scientific journal 
Nuclear Instruments and Methods A
and have presented the results at various conferences.  Since the commissioning of HELIOS, I have been closely involved with every experiment conducted with HELIOS. 


Based on my experience, detailed here and in the enclosed documents, I am a uniquely qualified candidate for this position.  I look forward to the possibility of returning to Argonne with my family. Thank you for your consideration.
}
\cfoot{}

\vspace{2.0\baselineskip}%triple space

{\setlength{\parindent}{0in}
Enclosures:
\vspace{2pt}%triple space
\begin{changemargin}{9pt}
\renewcommand{\arraystretch}{1.0} % set tabular line spacing
\begin{tabular}{ll}%
%Enclosures:
\statename & (2 page)\\%%
\refsname & (1 page)\\%
\cvname & (2 pages)\\
\pubname & (pages)\\
\end{tabular}%
\end{changemargin}
}