\cvwrapper{fancy}{Cover Letter}{

I am applying for one of the three postodoctoral research positions, Position \#038836--8.  I am currently employed as a postdoctoral research fellow at TRIUMF where I work in the Nuclear Physics Department in the Physical Science Division under the supervision of Dr.\ Barry Davids. Since October 2012, I have worked with Dr.\ Davids on the commissioning of the Electromagnetic Mass Analysier (EMMA), a heavy recoil spectrometer for nuclear reactions. 

\cfoot{}
%\clearpage
%%\newpage
%\cvwrapper{fancy}{\statename}{%
%Given below is my research statement.
%}
\pagestyle{fancy}

\phantomsection
\addcontentsline{toc}{chapter}{\statename}
%\begin{changemargin}{\indent}
%\nameaddress{\workaddress}%\\
%%\\\displaydate{letterdate}
%\end{changemargin}
%%-----------------------------------------------------------------------------------------------
\section*{Background}
\addcontentsline{toc}{section}{Background}
%%-----------------------------------------------------------------------------------------------
I have over thirteen years of experience in physics research, specializing in the technical development of new experimental hardware.
Starting in 2002 as an undergraduate, I helped establish thin film production facilities at Michigan State University and Albion College.
As a graduate student at Western Michigan University, the first three years of my research experience focused on two experiments measuring the pair-production branching ratio of the Hoyle state in $^{12}$C using a novel plastic scintillator array.  As a part of this work, I learned to operate the 6\,MeV tandem Van de Graaff accelerator at WMU.  In addition to the typical duties associated with running an experiment---detector setup, data acquisition, and analysis---I also was responsible for designing and machining the detector mounts.% that were used.
%During this time I was also collaborating on a number of experiments at Argonne National Laboratory; these experiments measured transfer reactions on radioactive beams produced in-flight and were measured with an array of double-sided silicon strip detectors.

I began full-time work at Argonne in July 2007 and the last four years of my doctoral thesis work involved the
 development, commissioning, and operation of the Helical Orbit Spectrometer (HELIOS).
 %I worked on nearly every aspect of the development of this new device since the MRI solenoid upon which it is based was delivered to the lab.  One of my first responsibilities was measuring and analyzing a high-resolution field map of the HELIOS solenoid.  I assembled most of the mechanical structures associated with the spectrometer and was involved in the design of many of the mechanical components.
%I designed and constructed the electronics readout, including fabricating most of the cables.
In addition to the substantial technical aspects of this project,
 a major component of my work was the development of computer code. % for the acquisition, calibration, simulation, and analysis of HELIOS data. 
%Since the commissioning of HELIOS, I have been closely involved with every experiment conducted with HELIOS. 
%  \textit{more details here}  
 %a major component of my work was the development of computer code associated with %data acquisition.  
%HELIOS.
I wrote and developed particle tracking simulations, %for optimizing experimental setups.
% and developed a pre-existing Monte Carlo simulation. 
%I also wrote the basis of the
 the data acquisition code, and % that is still in use today and I established and developed
 the calibration and analysis algorithms for data acquired with HELIOS. 
 I also wrote the proposals for the first two HELIOS experiments and published the results of the first experiment.
%After HELIOS was commissioned, % and into my postdoc appointment,
As a postdoc at Argonne, 
 I continued to collaborate on %    and have been involved with the setup and running of every 
the setup, calibration, and analysis of HELIOS experiments, as well as %. %since then. %commissioning 
%I have also helped with the  (both online and offline) of several HELIOS experiments.
%A HELIOS-like spectrometer at FRIB is the ideal device for studying transfer reactions with re-accelerated exotic beams.  
%Most of the measurements made with HELIOS have been of transfer reactions with radioactive beams.
%At the same time, I also collaborated on
 a variety of experiments using the Enge split-pole spectrograph.% During these experiments, it was typically my responsibility to set up the detector electronics and data acquisition 

Since October 2012,
I have been a postdoctoral research fellow at TRIUMF where I am working
% in the Nuclear Physics Department in the Physical Science Division under the supervision of Dr.\ Barry Davids.  I have worked with Dr.\ Davids 
on the commissioning of the EMMA %Electromagnetic Mass Analysier (EMMA), a heavy recoil 
spectrometer. % for nuclear reactions.
 One of my main responsibilities has been the characterization and commissioning of EMMA's two gas-filled detectors. %Over the last several months
 I have been developing code for the acquisition, calibration, simulation, and analysis of data from the EMMA parallel-grid avalanche counter and ionization chamber. % detector based on two in-beam tests.
As a part of this work I wrote an extensive safety review of the EMMA gas-handling system. I have also been involved with a number of laborious tasks related to the mechanical development of the spectrometer, including the polishing and assembly of  electrostatic components and the installation of radiation shielding.
%; % September 2013--January 2014,
		%designed the detector readout electronics. %January 2013
		%Supervised student projects.
		During my time at TRIUMF,  I have also collaborated on several IRIS experiments and one TUDA experiment, providing online data analysis.
		 As the installation of EMMA draws near, I have been working on developing the  spectrometer's burgeoning scientific program.	Most recently, I have been writing and reviewing %wrote the 
		experimental proposals for EMMA's radioactive beam commissioning.

%%-----------------------------------------------------------------------------------------------
%% Interests
%%-----------------------------------------------------------------------------------------------
%\pagebreak[4]
\section*{Interests}
\addcontentsline{toc}{section}{Interests}
My research interests reflect my research experience, namely nuclear structure and nuclear astrophysics.  More specifically, my immediate 
research interests include %nuclear structure and
 the evolution of single particle states far from stability at the extremes of neutron excess and nucleosynthesis in the classical \textit{r}-process. % and the ``cold'' \textit{r}-process (discussed below).
 In many cases, the study of structure
and astrophysics go hand-in-hand. For example, %such as 
near the $N=50$ and $N=82$ neutron shells,  
an experiment from which 
the energy, spin and parity of nuclear states can be derived may allow for the determination of the 
the single particle structure of the nucleus and serve as an input to 
%states  with the investigations related to the 
$r$-process%. For example, 
network calculations 
, which
 rely on these quantities as inputs. %the energy and spectroscopic factors of single particle states.

The synthesis of approximately half of the chemical elements heavier than zinc % ($A \simeq 70$)
 occurs in the rapid neutron-capture process.
The exact site of the $r$-process is unknown, but the conditions of 
%The elucidation of the site of the %this so-called
 %$r$-process is one of the most important scientific challenges in astrophysics. 
the ``classical'' $r$-process %is a site-free model %approach
% which assumes
are a hot environment ($T> 1.35$\,GK) with neutron densities beyond %$1\times 
$10^{20}$\,cm$^{-3}$. %and
%Classical calculations have been carried out in
In the waiting-point approximation, equilibrium %is achieved
 between neutron capture and photodisintegration %$(n,\gamma)\rightleftharpoons(\gamma,n)$ 
 %in isotopic chains. %is achieved.
%In this approach, the reaction path can be  calculated for a given temperature and neutron density via the Saha equation.
% During equilibrium,
implies that  the neutron capture rates do not play a role %under these assumptions since
in shaping the final $r$-process abundance curve.
%because they are balanced by the photodisintegration reaction rates. 
% In classical calculations, during most of the $r$-process, $n$-capture rates are irrelevant because these reactions are fast enough to establish equilibrium with photodisintegration.
However, there has been recent interest in so-called
 ``cold'' $r$-process scenarios in which the 
%at later %\correction{}{r}
 %times when 
the temperature and the neutron density 
are insufficient to
%drop, % ("freeze-out phase"),
%equilibrium can no longer be maintained, $n$-capture rates on a number of unstable nuclei have appreciable effects on the shapes of the predicted abundance distributions.
%Recent work suggests that there may be two sites for producing nuclei previously attributed to a single $r$-process.
%: %\correction{,}{:}
 %merging neutron stars and core collapse supernovae. 
 %While the temperature and neutron density in % in, and entropy in %the former 
 %neutron star mergers appear to be appropriate for synthesizing the heaviest nuclei, the neutrino-driven wind core collapse supernova hypothesis does not result in the electron fractions and entropies needed to produce significant quantities of nuclei with $A\gtrsim130$.
 %However, the observations of $r$-process elements in metal-poor stars cannot easily be explained by 
 %neutron star mergers, which would  occur neither on short enough timescales nor frequently enough to account for the observations \cite{Qian_2000,Argast_2004}. 
% An alternative core collapse supernova $r$-process scenario has recently been proposed % by \citet{Banerjee_2011,Banerjee_2013} %\correction{Banerjee, Qian, Heger, and Haxton}{\citet{Banerjee_2013}} % 
%to take place in the He shell of a massive star that has undergone core collapse. 
%These %so-called
 %``cold'' $r$-process scenarios
% are not hot enough to %no longer 
 reach the ($\gamma,n)\rightleftharpoons(n,\gamma)$ equilibrium. In these scenarios, the $\beta$-decay rates are in equilibrium with neutron capture rates, which %drives the reaction path much further neutron-rich and
 requires general knowledge of neutron capture rates of neutron-rich isotopes to determine the  $r$-process abundances.
% free neutrons %or neutrons which are released from the neutron-rich progenitors via $\beta$-delayed neutron emission 
%can be captured and thus shape the final $r$-process abundance curve.


Direct measurements are impossible in these cases because  the required radioactive targets cannot be produced. Instead, transfer reactions such as $(d,p)$ measurements in inverse kinematics are needed to determine neutron spectroscopic factors, spins, parities, and energies of the relevant states so that the neutron capture cross sections can be calculated.
%At the neutron densities of $\sim10^{19}$\,cm$^{-3}$ found in the He shell $r$-process model,
While studies of nuclei relevant to the classical $r$-process may need to wait for facility upgrades, the nuclei synthesized in cold %the He shell 
$r$-process model %, %cold $r$-process 
are closer to the valley of $\beta$-stability % than in the classical $r$-process 
and are %therefore now
within reach %at ISAC from proton-induced fission of a UC$_x$ target. 
of existing facilities.
%The relatively low temperatures found in the He shell imply that ($\gamma,n)\rightleftharpoons(n,\gamma)$ equilibrium is never
%reached and as a result %therefore
% neutron capture cross sections have a large influence on final predicted abundances.
A particularly important ingredient of calculations of the ``cold'' $r$-process %this model is %therefore
is
the neutron capture cross sections of nuclei with $Z>26$ and $50<N<82$. Experimental data for cases around closed shells are vital for ensuring the reliability of structure models needed to extrapolate to unmeasured nuclei. As the level density of nuclei near closed shells is anticipated to be low, statistical model calculations may be unreliable and must be tested. %cannot be trusted.
% of transfer reaction measurements to study the systematic   %Deriving neutron-capture cross sections via neutron-transfer reactions will provide important insight into astrophysical nucleosynthesis.

\rhead{\desctext{\statename}}
%\cfoot{\thepage{}  of \pageref{LastPage}}

%%-----------------------------------------------------------------------------------------------
%% Goals
%%-----------------------------------------------------------------------------------------------
\section*{Goals}
\addcontentsline{toc}{section}{Goals}
In the near term, my research goals at LSU will be the installation, characterization, and commissioning of the 
Enge split-pole spectrograph %from Yale 
at the accelerator facility at Florida State University.
In addition, I plan on aiding the further development of the ANASEN detector array. 
ANASEN has already proven to be a powerful tool for nuclear spectroscopy---particularly in it ability to measure excitation functions---and is an important part of the suite of equipment at the RESOLUT facility at FSU and the ReA3 facility at Michigan State University. 

%The recent availability of the new $^3$H target, a number of reactions in inverse kinematics are now possible that %using stable beams that 
%allow access to nuclei about which very little is know. Two examples relevant to the ``cold'' $r$-process are $^{87}$Rb($t$,$p$)$^{89}$Rb and $^{86}$Kr($t$,$p$)$^{88}$Kr. Both of these reactions utilize stable beams of $N=50$ nuclei. In both cases, the resultant nuclei have 
%%The nucleus $^{88}$Kr has 
%only once been studied previously using a quasielastic transfer reaction and relatively little is known in the region of the neutron separation energy of $\textrm{S(n)}\sim 7$\,MeV.
%
%Many of the reactions of interest for the classical $r$-process, such as ($d$,$p$) reactions near the $^{132}$Sn doubly-magic shell closure, require radioactive beam intensities not yet available. However, the planned 
%intensity upgrades for the
%CARIBU ion source will make many of these %radioactive
 %beams available, particularly in the $A \geq 130$ region. Once these beams are available, studying them with transfer reactions would be one of my research priorities. 

%%the development of the surrogate reaction technique for the determination of
%%reaction yields along the s-, rp- and r-process paths. 

The  network of collaborators that I have developed at Argonne and TRIUMF provides the opportunity of collaborating on a number of upcoming experiments, especially in light of the imminent commissioning of the EMMA spectrometer and the start of its scientific program. Provided my schedule allows it, I plan on participating in the approved EMMA experiments and proposing an additional experiment.

\vspace{1.0\baselineskip}%triple space
Based on my experience% and my research plan
, detailed here and in the enclosed documents, I am a uniquely qualified candidate for this position.  I have a decade of experience related to the commissioning of nuclear spectrometers and the operation of charged particle detectors. I look forward to the possibility of applying my expertise to the commissioning activities %of the new spectrometer 
at FSU. Thank you for your consideration. 
}

\vspace{2.0\baselineskip}
{\setlength{\parindent}{0in}
Enclosures:
\vspace{2pt}%triple space
\begin{changemargin}{9pt}
\renewcommand{\arraystretch}{1.0} % set tabular line spacing
\begin{tabular}{ll}%
%Enclosures:
%\statename & (2 page)\\%%
\refsname & (1 page)\\%
\cvname & (2 pages)\\
\pubname & (7 pages)\\
\end{tabular}%
\end{changemargin}
}