\cvwrapper{fancy}{Teaching Evaluations}{% 
\cfoot{}
\phantomsection
\addcontentsline{toc}{section}{Cover Letter}
%In addition to 
As detailed in my CV (included elsewhere), I have ten semesters of teaching experience working as a laboratory instructor and tutor at at Albion College and Western Michigan University
%worked as a teaching assistant
from 2001--2005.  %The majority of that experience involved activities such as grading papers and laboratory instruction.
% During my time at Western Michigan, I received three teaching awards, including
Based on my performance instructing laboratory sections as a teaching assistant at WMU, I was asked to be the %course instructor 
instructor of record for the Spring 2006 semester of Physics 107 Elementary Physics, an introductory survey class for non-majors.
Although the course was not intended for Physics majors, the course was specifically required by the 
Aviation Flight Science, 
Speech Pathology and Audiology, 
and 
Earth Science
programs. Students from these majors made up the majority of the class of 46 students.
%There were 46 students enrolled in the class 

Included below is the Instructor and Course Evaluation Report from the course I instructed (3 pages).
Overall, the students gave my teaching effectiveness a rating of 4.6 out of 5.
%My section of that class was the first to cover every chapter of the textbook and the average class grade was a full letter-grade higher than previous semesters.
The students in my class came from a variety of backgrounds and for many students this was their first physics class. I have also included a selection of individual comments from the Instructor and Course Evaluations (3 pages). These evaluations are from some of the students that required the most help in the class. These were the students that I had the most interaction with, inside and outside of class, and therefore most accurately represent an evaluation of my teaching.

At the time I taught the class, it was unusual for a teaching assistant to be the sole instructor for a lecture course. In response to my performance as an instructor, I received two teaching awards from the Physics Department during the Spring 2006 semester, the 2005--2006 Haym Kruglak Graduate Student Teaching Excellence Award and the 2005--2006 Department Graduate Student Teaching Effectiveness Award. I have included the Haym Kruglak award letter below.
}


%For evidence of my teaching effectiveness, I submit the attached documents: 1) the Haym Kruglak Award letter, 2) the summary of the Instructor and Course Evaluations from my lecture class, and 3) a selection of three individual Instructor and Course Evaluations from students.}
%
\vspace{2.0\baselineskip}%triple space
{\setlength{\parindent}{0in}
Enclosures:
\vspace{2pt}%triple space
\begin{changemargin}{9pt}
\renewcommand{\arraystretch}{1.0} % set tabular line spacing
\begin{tabular}{ll}%
Instructor and Course Evaluations Report & (3 pages)\\%
Selected Instructor and Course Evaluations Comments& (3 pages)\\%
Haym Kruglak Award letter & (1 page)\\%
\end{tabular}%
\end{changemargin}
}
\phantomsection
\addcontentsline{toc}{section}{Instructor Report}
\phantomsection
\addcontentsline{toc}{section}{Student Comments}
\phantomsection
\addcontentsline{toc}{section}{Award Letter}