I am applying for one of the faculty position in Experimental Nuclear Physics. The last four years of my doctoral thesis work involved the development, commissioning, and operation of the Helical Orbit Spectrometer (HELIOS) at Argonne National Laboratory.  In addition to the mechanical and technical aspects of this project, a major component of my work was the development of an  analysis algorithm for data acquired with HELIOS.  I have published the results of the commissioning of HELIOS in a scientific journal % Nuclear Instruments and Methods A
 and have presented the results at various conferences. My research plan at Central Michigan University, detailed in the attached Research Statement, would use my expertise with the HELIOS spectrometer at Argonne to help collaborate on the HELIOS@FRIB project.\\

I worked as a teaching assistant through all four years while at Albion College as an undergraduate.  While working as a graduate student at Western Michigan University, in addition to the standard teaching assistant responsibilities, I also taught a lecture class.   %It is unusual for a graduate student to teach a lecture class in the Physics Department at Wester Michigan and
 I was asked to teach a class by the department chair in response to the overwhelming positive feedback from students in my laboratory sections.  As a course instructor, my responsibilities included developing a curriculum, writing exams, and giving daily lectures.  While teaching at WMU as a laboratory instructor and course instructor, I received three different teaching awards.  A selection of student evaluations of my lecture class are included in the attached Evidence of Teaching Effectiveness document.\\

Based on my experience, detailed here and in the attached CV, I am a uniquely qualified candidate for this position.
Thank you for your consideration.