\renewcommand{\doctitle}{\shortname~\refsname}
\hypersetup{pdftitle=\doctitle}
\cvwrapper{fancy}{\refsname} {
Given below is my list of references; those people whom I have contacted for letters of recommendation.
Dr.\ Barry Davids has been my supervisor at TRIUMF since October 2012 and is my current employer. Most of my work with 
%I have been working with
 Dr.\ Davids has been focused on the %on the construction and
 commissioning of the EMMA spectrometer and the supervision of students.
I have worked with Dr.\ Martin Alcorta on a variety of experiments from May 2010 to July 2012 at Argonne and since October 2013 at TRIUMF. Most recently, I have collaborated with Dr.\ Alcorta on IRIS experiments and on EMMA commissioning activities.
Dr.\ Alan Wuosmaa was my doctoral thesis adviser. I worked for Dr.\ Wuosmaa from August 2004 until to July 2012, including a postdoctoral appointment, and I continue to collaborate with him today.  Most of my work with Dr.\ Wuosmaa has been related to the HELIOS spectrometer.
\cfoot{}
%Dr.\ Birger Back has been my supervisor at Argonne since July 2007.
%I worked with Dr.\ Catherine Deibel on a variety of experiments during her postdoc appointment at Argonne from 2008-2011.
%Dr.\ Paul Pancella was the department chair while I was a student at Western Michigan and it was he that appointed me to my teaching position as a course instructor.  If additional references are need, two more are given.  Scott Marley has been a colleague of mine at both Western Michigan and Argonne since August, 2004.  Finally, Larrs Morey was a student of mine while I was a course instructor.
}
\vspace{2.0\baselineskip}%triple space
{\setlength{\parindent}{0in}

\begin{multicols}{2}

\boldtext{Barry Davids}\\
Research Scientist\\
TRIUMF\\
4004 Wesbrook Mall\\
Vancouver, BC\hspace{6pt}V6T~2A3\\
Canada\\
(604) 222-7396\\
\href{mailto:davids@triumf.ca}{davids@triumf.ca}\\

\boldtext{Martin Alcorta}\\
ISAC Detector and Target Physicist\\
TRIUMF\\
4004 Wesbrook Mall\\
Vancouver, BC\hspace{6pt}V6T~2A3\\
Canada\\
(604) 222-7419\\
\href{mailto:malcorta@triumf.ca}{malcorta@triumf.ca}\\
\columnbreak

\boldtext{Alan H. Wuosmaa}\\
Professor of Physics\\
Department of Physics\\
University of Connecticut\\
2152 Hillside Road, U-3046\\
Storrs,  CT 06269-3046\\
United States\\
(860) 486-4693\\
\href{mailto:alan.wuosmaa@uconn.edu}{alan.wuosmaa@uconn.edu}\\

%\boldtext{name}\\
%title\\
%institute\\
%address\\
%city\\
%country\\
%telephone\\
%\href{mailto:email}{email}

%\boldtext{Birger Back}\\
%Senior Physicist\\
%Physics Division\\
%Argonne National Laboratory\\
%Argonne, IL 60439\\
%(630) 252-3618\\
%\href{mailto:back@anl.gov}{back@anl.gov}\\

%\boldtext{Catherine Deibel}\\
%Assistant Professor of Physics\\
%Department of Physics \& Astronomy\\
%Louisiana State University\\
%218-B Nicholson Hall, Tower Dr.\\
%Baton Rouge, LA 70803-4001\\
%(225) 578-4950\\
%\href{mailto:deibel@phys.lsu.edu}{deibel@phys.lsu.edu}

%\boldtext{Paul Pancella}\\
%Professor of Physics\\%, former chair\\
%Department of Physics\\
%Western Michigan University\\
%Kalamazoo MI, 49008-5252\\
%(269)-387-4962\\
%\href{mailto:paul.pancella@wmich.edu}{paul.pancella@wmich.edu}\\
%
%\columnbreak
%\boldtext{Scott Marley}\\
%Physics Division\\
%Argonne National Laboratory\\
%Argonne, IL 60439\\
%(630) 252-7647\\
%\href{mailto:scott.t.marley@wmich.edu}{scott.t.marley@wmich.edu}\\
%
%\boldtext{Larrs Morey}\\
%(269) 329-4736\\
%\href{mailto:larrs8@hotmail.com}{larrs8@hotmail.com}\\
\end{multicols}
}
