\cvwrapper{fancy}{List of References}{
Given below is a list of references.  I have worked in physics research with Dr. Alan Wuosmaa since August, 2004; in addition, he was my doctoral thesis advisor and is my current employer.  Dr.\ Birger Back has been my supervisor at Argonne since July 2007.  Dr. Paul Pancella was the department chair while I was a student at Western Michigan and it was he that appointed me to my teaching position as a course instructor.  If additional references are need, two more are given.  Scott Marley has been a colleague of mine at both Western Michigan and Argonne since August, 2004.  Finally, Larrs Morey was a student of mine while I was a course instructor.
}

\begin{multicols}{2}
\textbf{Alan H. Wuosmaa}\\
Professor of Physics\\
Department of Physics\\
Western Michigan University\\
Kalamazoo MI, 49008-5252\\
(269) 387-4911\\
\href{mailto:alan.wuosmaa@wmich.edu}{alan.wuosmaa@wmich.edu}\\

\textbf{Birger Back}\\
Senior Physicist\\
Physics Division\\
Argonne National Laboratory\\
Argonne, IL 60439\\
(630) 252-3618\\
\href{mailto:back@anl.gov}{back@anl.gov}\\

\textbf{Paul Pancella}\\
Professor of Physics\\%, former chair\\
Department of Physics\\
Western Michigan University\\
Kalamazoo MI, 49008-5252\\
(269)-387-4962\\
\href{mailto:paul.pancella@wmich.edu}{paul.pancella@wmich.edu}\\

\columnbreak
\textbf{Scott Marley}\\
Physics Division\\
Argonne National Laboratory\\
Argonne, IL 60439\\
(630) 252-7647\\
\href{mailto:scott.t.marley@wmich.edu}{scott.t.marley@wmich.edu}\\

\textbf{Larrs Morey}\\
(269) 329-4736\\
\href{mailto:larrs8@hotmail.com}{larrs8@hotmail.com}\\


%\twocolumn
\end{multicols}